### 2017-06-05 paper/documents/2.background.tex
- update paper

\textit{Dota 2} map layout split into three lanes. Each lanes has three defensive towers. the Dire lanes and the Radiant lanes are quite different. the top of Radiant it is called off-lane , meanwhile in Dire, the top lane is called safe-lane. The bottom lane of Radiant is called safe-lane, while in Dire it is called off-lane. And the middle lane will remain same.

@@

Player roles or play styles is the way how player will choose and try to act as their roles or styles in the games. It is important to note that these roles describe a different facet of play than classic player type classifications (e.g. after Bartle \cite{bartle1996hearts}) which aim to classify expressed character traits of the players and were designed to match role-play style games. Comparison of videos, Online guides, and commentary of professional players and commentators are our sources for selection and characterization of the player roles. Player roles definitions and naming conventions will in any case differ slightly among the player base and shift over time as the game evolves, constituting another challenge for \textit{Machine Learning} applications in this area. We isolated five player roles for the main \textit{Machine Learning} task, which strike a balance between covering common play styles in great detail while leaving out some exotic styles which are rarely observed or are minor variations of the other styles. The isolated roles were: \textit{Carry} - who are usually weak and need protection early on, but are very strong in later stages, often deciding games. Carry typically end up with a high amount of last hits, gold per minute and overall kills, but they can get them in quite different ways.

>>>>

\textit{Dota 2} map layout split into three lanes. Each lanes has three defensive towers (see figure \ref{fig:map_lane}). the Dire lanes and the Radiant lanes are quite different. the top of Radiant it is called off-lane , meanwhile in Dire, the top lane is called safe-lane. The bottom lane of Radiant is called safe-lane, while in Dire it is called off-lane. And the middle lane will remain same.

@@

Player roles or play styles is the way how player will choose and try to act as their roles or styles in the games. It is important to note that these roles describe a different facet of play than classic player type classifications (e.g. after Bartle \cite{bartle1996hearts}) which aim to classify expressed character traits of the players and were designed to match role-play style games. Comparison of videos, Online guides, and commentary of professional players and commentators are our sources for selection and characterization of the player roles. Player roles definitions and naming conventions will in any case differ slightly among the player base and shift over time as the game evolves, constituting another challenge for \textit{Machine Learning} applications in this area. We isolated five player roles for the main \textit{Machine Learning} task, which strike a balance between covering common play styles in great detail while leaving out some exotic styles which are rarely observed or are minor variations of the other styles. The isolated roles were: \textit{Carry} - who are usually weak and need protection early on, but are very strong in later stages, often deciding games. Carry typically end up with a high amount of last hits, gold per minute and overall kills, but they can get them in quite different ways. \textit{Mid Laner} - this kind of playing style mostly will get middle lane position since early game. focusing on collecting more gold to obtain high percentage lane of gold in early ten minutes. \textit{Offlaner} - safe lane as their common lane. \textit{Dire} jungle is safe lane for dire team, otherwise the \textit{Radiant} jungle is safe lane for radiant team. Usually have balance between \textit{networth} and efficiently lane gold in early ten minutes. \textit{Roaming Support} - support heroes mostly weak, roaming support will have roaming attribute from replay file, this player roles will buy support item such as: \textit{Observer ward} and \textit{Sentry ward} for vision. \textit{Hard Support} - sometimes called babysitter, because this playing style need to do everything for supporting the Carry. Mostly, buy support items much more than roaming support.

### 2017-06-05 paper/documents/4.experiment.tex
- update paper

\subsection{Attribute Construction and Evaluation}
\label{sec:attconsandeval}
Attributes for evaluation is presented in table \ref{table:table1}. While some attributes correspond directly to summary data, attributes that capture positional information the fighting behavior require more complex processing of the replay data. Different attribute filters implemented in the Java library WEKA \cite{hall2009weka} to determine the best set of attributes. Our results with the \textit{WrapperSubsetEval} class with best-first search are presented in table 1. We have chosen this algorithm for our final attribute selection because it resulted in the highest accuracy with our labeled data set. For classification we selected all attributes that were present in at least four folds, excluding assists, as this resulted in the overall highest accuracy. In the following sections we describe the algorithms and heuristics we developed to calculate the attributes that cannot be directly obtained from replay files. They can be grouped into five rough categories: space and movement, early ganks, team fights, support items, and damage types. Not all of the attributes we describe in this section were finally chosen to be used for classification within this work but they might prove valuable for future works.

\subsection{Space and Movement}
\label{spaceandmovement}

\begin{figure}
\centering
\includegraphics[width=2.5in]{./figures/lane_map.png}
\caption{\textit{Dota 2} map designed with three lane. Top lane, middle lane and also bottom lane.}
\label{fig:map_lane}
\end{figure}

Most of player roles depend on the lane (see figure \ref{fig:map_lane}) which is the most active in the early game. Player lane information also provides the constructor for the other attributes, e.g., the \textit{lane partners}. In the early game, players commonly have three main positions: \textit{top lane}, \textit{mid lane}, or \textit{bottom lane}. In additional, the \textit{jungle} areas also can be used ( see figure \ref{fig:map_jungle}). Or, players can have a \textit{roaming} position, it means that they will move around the map instead of focusing in specific lane.

\begin{figure}
\centering
\includegraphics[width=2.5in]{./figures/map_jungle.png}
\caption{\textit{Dota 2} map jungle areas divided into two areas, \textit{Dire} and \textit{Radiant} jungle.}
\label{fig:map_jungle}
\end{figure}

@@

>>>>

\subsection{Attribute Construction and Evaluation}
\label{sec:attconsandeval}

Attributes for evaluation is presented in table \ref{table:table1}. While some attributes correspond directly to summary data, attributes that capture positional information the fighting behavior require more complex processing of the replay data. Different attribute filters implemented in the Java library WEKA \cite{hall2009weka} to determine the best set of attributes. Our results with the \textit{WrapperSubsetEval} class with best-first search are presented in table 1. We have chosen this algorithm for our final attribute selection because it resulted in the highest accuracy with our labeled data set. For classification we selected all attributes that were present in at least four folds, excluding assists, as this resulted in the overall highest accuracy. In the following sections we describe the algorithms and heuristics we developed to calculate the attributes that cannot be directly obtained from replay files. They can be grouped into five rough categories: space and movement, early ganks, team fights, support items, and damage types. Not all of the attributes we describe in this section were finally chosen to be used for classification within this work but they might prove valuable for future works.

\begin{figure}
\centering
\includegraphics[width=1.5in]{./figures/lane_map.png}
\caption{\textit{Dota 2} map designed with three lane. Top lane, middle lane and also bottom lane.}
\label{fig:map_lane}
\end{figure}

\textbf{Player Lane} Most of player roles depend on the lane (see figure \ref{fig:map_lane}) which is the most active in the early game. Player lane information also provides the constructor for the other attributes, e.g., the \textit{lane partners}. In the early game, players commonly have three main positions: \textit{top lane}, \textit{mid lane}, or \textit{bottom lane}. In additional, the \textit{jungle} areas also can be used ( see figure \ref{fig:map_jungle}). Or, players can have a \textit{roaming} position, it means that they will move around the map instead of focusing in specific lane.

\begin{figure}
\centering
\includegraphics[width=1.5in]{./figures/map_jungle.png}
\caption{\textit{Dota 2} map jungle areas divided into two areas, \textit{Dire} and \textit{Radiant} jungle.}
\label{fig:map_jungle}
\end{figure}

@@

\textbf{Lane Partners and Solo Lane} To calculate the lane attribute from lane partners and solo lane can be determine by comparing the number of players. Player in \textit{jungle} position or \textit{roaming} are always assigned with zero lane partners, while players who is sharing the other lane, such as top, mid or bottom lane are corresponding with number of their \textit{teammates} in the current lane. Solo lane attribute included in our attributes as an alternative to the lane partners. The value of this attribute will be true if a player is assigned to one of the tree main lanes without any teammate and otherwise false.

\textbf{Support Items} Player who considering playing as support mostly must buy support items. Many items in \textit{Dota 2} are useful for support player. List of common suppor items: \textit{Courier}, \textit{Flying Courier}, \textit{Observer Ward} and \textit{Sentry Ward}.

\textbf{Damage Types} We categorized damage type based on player roles and requirement of other attributes: damage to tower, damage to heroes, damage to regular creeps, damage to neutral creeps and damage to ancient creeps.

\subsection{Feature Normalization}
\label{sec:featurenorm}

We applied feature normalization on this paper in order to enhance high accuracy.
